---
title: "Homework 03: Probability"
subtitle: "Due: Friday, March 5 11:59pm ET"
author: "Navya Belavadi"
date: "03-05-2021"
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, 
                      warning = FALSE, comment = "#>", highlight = TRUE)
```

# Packages

```{r packages}
library(tidyverse)
```

# Part I

## Data

```{r data}
gamble <- read_table("http://users.stat.ufl.edu/~winner/data/riskgamble.dat",
                      col_names = FALSE)

gamble
```



#### Exercise 1

In this code chunk, I mutated gamble and created a tibble. 

```{r ex_1}
gamble <- rename(gamble, decision_1 = X1)
gamble <- rename(gamble, decision_2 = X2)
gamble <- rename(gamble, count = X3) %>%
  mutate(decision_1 = case_when(decision_1 == 1 ~ "A",
                                decision_1 == 2 ~ "B")) %>%
  mutate(decision_2 = case_when(decision_2 == 1 ~"C", decision_2 == 2 ~"D"))
gamble
```


#### Exercise 2

In this exercise, I computed the probability that a person chose "A" for 
Decision 1. 


```{r ex_2}
gamble %>%
  group_by(decision_1) %>%
  summarize(total_count = sum(count)) %>%
  mutate(sum_total_count = sum(total_count)) %>%
  filter(decision_1 == "A") %>%
  mutate(probability = total_count/sum_total_count) %>%
  select(decision_1, probability)
```

#### Exercise 3

Here, I computed the probability a person chose "A" and "D."


```{r ex_3}
gamble %>%
  mutate(total_count = sum(count)) %>%
  filter(decision_1 == "A", decision_2 == "D") %>%
  mutate(probability = count/total_count) %>%
  select(-count, -total_count)
```


#### Exercise 4

In this code chunk, I found the probability that a person who chose "B" for 
Decision 1 would choose "D" for Decision 2.

```{r ex_4}
gamble %>%
  filter(decision_1 == "B") %>%
  mutate(total_count = sum(count)) %>%
  mutate(probability = count/total_count) %>%
  filter(decision_2 == "D") %>%
  select(probability)
```


#### Exercise 5

In this exercise, I am to find the probability that a person who chose "B" for 
Decision 1 would choose "A" for Decision 2. This probability is 0, simply 
because it is not possible for Decision 2 to be anything besides C or D. 

#### Exercise 6

In this code chunk, I found the probability that a person who chooses "D" for 
Decision 2 chose "B" for Decision 1.

```{r ex_6}
gamble %>%
  filter(decision_2 == "D") %>%
  mutate(total_count = sum(count)) %>%
  mutate(probability = count/total_count) %>%
  filter(decision_1 == "B") %>%
  select(probability)
```


#### Exercise 7

If given the choice, I would select 

# Part II


```{r set_seed}
set.seed(2357822)
```

#### Exercise 8
In this exercise I am calculating the probability that someone would get 
matching numbers when drawing a card from a deck and rolling a 6-sided die. 

```{r ex_8}

results <- tibble(
  die = replicate(n = 10000, expr = sample(1:6, size = 1)),
  cards = replicate(n = 10000, expr = sample(2:14, size = 1)))
results <- results %>%
  mutate(event = die == cards)
results %>%
  summarize(probability = mean(event))
```



#### Exercise 9
In this exercise I find the probability that someone would get a face card or 
6 on a die upon drawing a card from a deck and rolling a 6-sided die. 

```{r ex_9}
results <- tibble(
  die = replicate(n=10000, expr=sample(1:6, size=1)),
  cards = replicate(n=10000, expr=sample(2:14, size=1)))
results <- results %>%
  mutate(event = (die == 6 | cards == 11:13))
results %>%
  summarize(probability = mean(event))
```


#### Exercise 10

In this code chunk I find the probability that all 3 cards drawn from
a deck sequentially are in increasing order, with ties not counting. 
```{r ex_10}
results <- tibble(
  cards_1 = replicate(n=10000, expr=sample(2:14, size=1)),
  cards_2 = replicate(n=10000, expr=sample(2:14, size=1)),
  cards_3 = replicate(n=10000, expr=sample(2:14, size=1))
)
results <- results %>%
  mutate(event = cards_3 > cards_2 & cards_2 > cards_1)
  results %>%
    summarize(probability=mean(event))
```


