---
title: "Homework 03: Probability"
subtitle: "Due: Friday, March 5 11:59pm ET"
author: ""
date: ""
output:
  pdf_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, message = FALSE, 
                      warning = FALSE, comment = "#>", highlight = TRUE)
```

# Packages

```{r packages}
library(tidyverse)
```

# Part I

## Data

```{r data}
gamble <- read_table("http://users.stat.ufl.edu/~winner/data/riskgamble.dat",
                      col_names = FALSE)

gamble
```

```{r}
gamble <- rename(gamble, decision_1 = X1)
gamble <- rename(gamble, decision_2 = X2)
gamble <- rename(gamble, count = X3) %>%
  mutate(decision_1 = case_when(decision_1 == 1 ~ "A",
                                decision_1 == 2 ~ "B")) %>%
  mutate(decision_2 = case_when(decision_2 == 1 ~"C", decision_2 == 2 ~"D"))
gamble
```


#### Exercise 1

In this code chunk, I mutated gamble and created a tibble. 

```{r ex_1}
gamble %>%
  group_by(decision_1) %>%
  summarize(total_count = sum(count)) %>%
  mutate(sum_total_count = sum(total_count)) %>%
  filter(decision_1 == "A") %>%
  mutate(probability = total_count/sum_total_count) %>%
  select(decision_1, probability)
```

#### Exercise 2

In this exercise, I computed the probability that a person chose "A" for 
Decision 1. 

```{r ex_2}
gamble %>%
  mutate(total_count = sum(count)) %>%
  filter(decision_1 == "A", decision_2 == "D") %>%
  mutate(probability = count/total_count) %>%
  select(-count, -total_count)
```

#### Exercise 3

Here, I computed the probability a person chose "A" and "D."

```{r}
gamble %>%
  filter(decision_1 == "B") %>%
  mutate(total_count = sum(count)) %>%
  mutate(probability = count/total_count) %>%
  filter(decision_2 == "D") %>%
  select(probability)
```

#### Exercise 4

In this code chunk, I found the probability that a person who chose "B" for 
Decision 1 would choose "D" for Decision 2.

```{r}
gamble %>%
  filter(decision_2 == "D") %>%
  mutate(total_count = sum(count)) %>%
  mutate(probability = count/total_count) %>%
  filter(decision_1 == "B") %>%
  select(probability)
```


#### Exercise 5

#### Exercise 6

#### Exercise 7

# Part II

#### Exercise 8

#### Exercise 9

#### Exercise 10

```{r set_seed}
set.seed(2357822)
```

